---
title: "Pagedown"
output:
  pagedown::html_letter:
    self_contained: false
links-to-footnotes: true
paged-footnotes: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(palmerpenguins)
```

::: from
Charlie Joey Hadley  
Bristol  
United Kingdom  
Email: charlie@rfortherestofus.com  
:::

# Intro

[{pagedown}](https://github.com/rstudio/pagedown) is designed to solve an annoying problem in RMarkdown

> Formatting PDF RMarkdown documents is difficult and requires LaTeX.

The {pagedown} solution is to allow us to write HTML documents with pagination (and printing) as the primary goal. It's really very good at it:

- pagedown::thesis_paged

- pagedown::jss_paged

- pagedown::html_resume

- pagedown::poster_relaxed

- pagedown::business_card

The **best** choice for creating multiple columns in {pagedown} is flexbox because it's browser width agnostic.

As before, we can use either `<div>` tags or `:::`

## Using ::: {.page-break-before}

:::: {style="display: flex;"}

::: {}

This is the first column (on the left)

```{r}
penguins %>% 
  ggplot(aes(x = bill_length_mm,
             y = bill_depth_mm,
             color = species)) +
  geom_point()
```

:::

::: {}

... and this is the second column (on the right)

```{r}
penguins %>% 
  ggplot(aes(x = bill_length_mm,
             y = bill_depth_mm,
             color = island)) +
  geom_point()
```

:::

::::

## Using `<div>`

<div style="display: flex;">

<div>

This is the first column (on the left)

```{r}
penguins %>% 
  ggplot(aes(x = bill_length_mm,
             y = bill_depth_mm,
             color = species)) +
  geom_point()
```

</div>

<div>

... and this is the second column (on the right)

```{r}
penguins %>% 
  ggplot(aes(x = bill_length_mm,
             y = bill_depth_mm,
             color = island)) +
  geom_point()
```

</div>

</div>









